UQWorld: an Applied UQ Community

### 2019-05-08 latex/uqworld-presentation.tex
Update slides

% Users need help, they might demand something, and some are ready to give back.
% Audience from users is readily available (_you build it, and they will come_).
Many user online communities started as support communities, but if \emph{only} for that:
\begin{itemize}
  \item it'll be too restrictive % If UQ is somehow already a niche, then UQLab users would even be smaller bunch of audience. We attached too much the growth of the community with the growth of UQLab. Finally, there are times that you yourself would be more interested talking about UQ than just UQLab.
  \item it's not very aspiring
\end{itemize}
%\\~\\
Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.
%\\~\\
Besides, there seems to be an opportunity...

@@

%===============================================================================
\begin{frame}[t]{What's next: A Community Cycle}

@@

\begin{enumerate}
  \item Accept the invitation and start browse around UQWorld.
  \item Familiarize yourself with structure and the mechanics of the platform.
  \item Reply to the topic \emph{First time in the forum? Welcome!}
  \item Start thinking about some of your external colleagues, how they might benefit from joining UQWorld.
  \item Start thinking about what kind of conversation or things you want to bring or share here.
\end{enumerate}

@@

\begin{enumerate}
  \item For certain things, instead of sharing and discussing with the group by email, create a topic in UQWorld (but you can start early too!). 
  \item Send personal invitation emails to your external colleagues, why they should join UQWorld (but only if you think they should).
  \item If you still receive UQLab support email, refer the sender to UQWorld.
  \item Regularly check UQWorld (ps: community manager will notify you separately if there's something of interest)
\end{enumerate}

>>>>

% Users need help, they might demand something, and some are ready to give back.
% Audience from users is readily available (_you build it, and they will come_).
Many user online communities started as support communities, but if \emph{only} for that:
\begin{itemize}
  \item it'll be too restrictive % If UQ is somehow already a niche, then UQLab users would even be smaller bunch of audience. We attached too much the growth of the community with the growth of UQLab. Finally, there are times that you yourself would be more interested talking about UQ than just UQLab.
  \item it's not very aspiring
\end{itemize}

\vspace{0.3cm}

Widening the scope to applied UQ makes sense as there's potential audience wider than UQLab users.

\vspace{0.3cm}

Besides, there seems to be an opportunity...

@@

%===============================================================================
\begin{frame}[t]{What's next: An online community lifecycle}

\begin{tabularx}{\textwidth}{XXXX}
  \hline
                                    & Inception    & Establishment  & Maturity \\
  \hline
  \footnotesize{Majority of members}
  & Core members
  & UQLab users, UQ practitioners
  & UQ practitioners and researchers  \\

  \footnotesize{Activity by comm. manager, core members}
  & $50$\%-$100$\%
  & $10$\%-$50$\% 
  & $<10$\% \\

  \footnotesize{Growth rate by word-of-mouth}
  & $0$\%-$50$\% 
  & $50$\%-$90$\%
  & $>90$\% \\

  \footnotesize{Why members join}
  & Relationship with core members, problems with UQLab
  & matched interests in UQ, tangible value (info, support)
  & Tangible value: info, support, and social (incl. sharing expertise) \\
%  \footnotesize{Example of tasks}
%  & Define scope and goal, invite members, initiate discussions, prompt participation
%  & Write contents (about the community), organize \emph{activities} 
%  & off-line gatherings, manage volunteer (non core members)  \\ 
  \hline
\end{tabularx}

\vspace{0.35cm}

\emph{Critical mass}: $\geq 50\%$ activities and $\geq 50\%$ growth rate
are by the community members themselves.

@@

\begin{enumerate}
  \item Accept the invitation and start browse around UQWorld.
  \item Familiarize yourself with structure and the mechanics of the platform.
  \item Reply to the topic \emph{First time in the forum? Welcome!}
  \item Start thinking about some of your external colleagues, how they might benefit from joining UQWorld.
  % Benefit here means getting help, sharing expertise, or both.
  \item Start thinking about what kind of conversation or things you want to bring or share here.
\end{enumerate}

@@

\begin{enumerate}
  \item For certain things, instead of sharing and discussing by email, create a topic in UQWorld (you can start early too!).  % That way we can get the conversation going.
  \item Send personal invitations to your external colleagues, why they should join UQWorld (but only if you think they should).
  \item If you still receive UQLab support email, refer the sender to UQWorld.
  \item Regularly check UQWorld (ps: community manager will prompt you separately if there's something of interest).
\end{enumerate}
